---
title: "Anderson-Darling Test"
author: "Lillian Holden"
date: "2023-10-19"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Anderson Darling Introduction

The Anderson Darling test is a form of the Goodness of Fit test used to determine if a sample of data came from a specific kind of distribution. It is commonly used to determine if the sample of data came from a normal distribution. It is a modification of the Kolmogorov-Smirnov test that gives more weight to the tails. This means ...

H0 is the data that follows a specific distribution
HA is the data that does not follow the specific distribution 

The equation is as follows:

A^2 = -N-S

where S=N∑i=1((2i−1)/N)(lnF(Yi)+ln(1−F(YN+1−i)) 

F is the cumulative distribution function of the specified distribution.
Yi is the ordered data. 

The test is useful to test normality which is common for regression, ANOVA, t-tests and more. 

To use the Anderson Darling function, you must install the package known as "nortest" and use the the ad.test() function. 

```{r}
install.packages("nortest")
library(nortest)
```
```{r}
#Create your own function that is normally distributed 
set.seed(1) #Use the set.seed() function to allow the data to repeatable
ndistribution <- rnorm(100, 25, 1) #The rnorm() function generates a random sample with a default mean of 0 and standard deviation of 1
ndistribution
```

## Perform the Anderson Darling Test on the Sample of Data using the ad.test() function
```{r}
ad.test(ndistribution)
```

```{r}
hist(ndistribution)
```


```{r}
set.seed(1)
nodistribution <- rpois(100, 25)
nodistribution
```

```{r}
hist(nodistribution)
```

```{r}
ad.test(nodistribution)
```

### Using the Anderson-Darling Test with Preset Normal Distribution Data Known as "Iris"
````{r}
set.seed(1)
d <- iris
d
```

x <- sort(d[complete.cases(d)])
    n <- length(x) #length must be greater than 7
logp1 <- pnorm((x - mean(x))/sd(x), log.p = TRUE)
    logp2 <- pnorm(-(x - mean(x))/sd(x), log.p = TRUE)
    h <- (2 * seq(1:n) - 1) * (logp1 + rev(logp2))
    A <- -n - mean(h)
    AA <- (1 + 0.75/n + 2.25/n^2) * A
    
### Then use this if AA < 0.2
pval <- 1 - exp(-13.436 + 101.14 * AA - 223.73 * AA^2
    
    
function (x) 
{
    DNAME <- deparse(substitute(x))
    x <- sort(x[complete.cases(x)])
    n <- length(x)
    if (n < 8) 
        stop("sample size must be greater than 7")
    logp1 <- pnorm((x - mean(x))/sd(x), log.p = TRUE)
    logp2 <- pnorm(-(x - mean(x))/sd(x), log.p = TRUE)
    h <- (2 * seq(1:n) - 1) * (logp1 + rev(logp2))
    A <- -n - mean(h)
    AA <- (1 + 0.75/n + 2.25/n^2) * A
    if (AA < 0.2) {
        pval <- 1 - exp(-13.436 + 101.14 * AA - 223.73 * AA^2)
    }
    else if (AA < 0.34) {
        pval <- 1 - exp(-8.318 + 42.796 * AA - 59.938 * AA^2)
    }
    else if (AA < 0.6) {
        pval <- exp(0.9177 - 4.279 * AA - 1.38 * AA^2)
    }
    else if (AA < 10) {
        pval <- exp(1.2937 - 5.709 * AA + 0.0186 * AA^2)
    }
    else pval <- 3.7e-24
    RVAL <- list(statistic = c(A = A), p.value = pval, method = "Anderson-Darling normality test", 
        data.name = DNAME)
    class(RVAL) <- "htest"
    return(RVAL)
