---
title: "Anderson-Darling Test"
author: "Lillian Holden"
date: "2023-10-19"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Anderson Darling Introduction

The Anderson Darling test is a form of the Goodness of Fit test used to determine if a sample of data came from a specific kind of distribution. It is commonly used to determine if the sample of data came from a normal distribution. It is a modification of the Kolmogorov-Smirnov test that gives more weight to the tails. This means ...

H0 is the data that follows a specific distribution
HA is the data that does not follow the specific distribution 

The equation is as follows:

A^2 = -N-S

where S=N∑i=1((2i−1)/N)(lnF(Yi)+ln(1−F(YN+1−i)) 

F is the cumulative distribution function of the specified distribution.
Yi is the ordered data. 

The test is useful to test normality which is common for regression, ANOVA, t-tests and more. 

To use the Anderson Darling function, you must install the package known as "nortest" and use the the ad.test() function. 

```{r}
install.packages("nortest")
library(nortest)
```
```{r}
#Create your own function that is normally distributed 
set.seed(1) #Use the set.seed() function to allow the data to repeatable
ndistribution <- rnorm(100) #The rnorm() function generates a random sample with a default mean of 0 and standard deviation of 1
ndistribution
```
## Perform the Anderson Darling Test on the Sample of Data using the ad.test() function
```{r}
ad.test(ndistribution)
```

```{r}
nodistribution <- c(1:100)
nodistribution
```

```{r}
ad.test(nodistribution)
```

